---
title: "spatialdata"
description: |
  A short description of the post.
author:
  - name: Alicia Fennell
    url: {}
date: 03-11-2021
output:
  distill::distill_article:
    self_contained: false
    code_folding: Code 
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)

library(tidyverse)
library(here)
library(janitor)
library(sf)
library(tmap)
library(gstat)
library(stars)
```

### Spatial data visualization 

This project uses data downloaded from the Office of Spill Prevention and Response (OSPR) Incident Tracking Database. Specifically, this project explores 2008 oil spills in California by county. An oil spill is defined as "a discharge or threatened discharge of petroleum or other deleterious material into the waters of the state" (Oil Spill Incident Tracking). 

```{r}

## Read in spatial data for oil spills and county boundaries

oil_spill <- read_sf("oil_data", "Oil_Spill_Incident_Tracking_%5Bds394%5D") %>% 
  clean_names()

ca_counties <- read_sf("ca_counties", layer = "CA_Counties_TIGER2016") %>% 
  clean_names()

## Check projections of both 
# st_crs(oil_spill)
# st_crs(ca_counties)

## These seemed like the same projection, but I'll transform just to make sure they are the same projection.

ca_counties <- st_transform(ca_counties, st_crs(oil_spill))
```

```{r}
## Interactive map to view oil spill locations 

tmap_mode("view")

#tm_basemap("Stamen.Watercolor") 
#tm_style("watercolor") +
tm_shape(ca_counties) +
  tm_borders("white") + 
  tm_shape(oil_spill) +
  tm_dots(size = .03, alpha = 0.5)

#, col = "red3")

```

***Figure 1.*** Oil spill locations in California during 2008. Click a point to see more details such as city and waterway of spill.  

```{r}
## Make a static chloropleth map where fill color depends on count of inland oil spill events by county 
## Filter for only inland spills and count by county 

oil_inland <- oil_spill %>% 
  filter(inlandmari == "Inland") %>% 
  count(localecoun) 

## Join the two datasets and plot them using geom_sf()

oil_joins <- ca_counties %>% 
  st_join(oil_inland)

ggplot() +
  geom_sf(data = oil_joins, aes(fill = n)) +
  scale_fill_gradientn(colors = c("wheat", "sienna2", "red3", "red4")) +
  theme_void() +
  labs(fill = "Number of Inland Oil Spills") +
  scale_x_continuous(breaks = c(50, 100, 150, 200, 250, 300))

```

***Figure 2.*** Number of inland oil spills per county in California during 2008. As seen by the dark red on the map, Los Angeles County experienced the most oil spills (340); the next highest was San Mateo County with 173 spills. Modoc County (top right) had no recorded oil spills in 2008.  
