---
name: Alicia
surname: Fennell
position: "Master's Student in Environmental Science & Management"
address: "Santa Barbara, CA"
phone: "(805) 450-5148"
email: "aliciafennell@bren.ucsb.edu"
github: aliciafennell
linkedin: alicia-fennell
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::moderncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# About me  

I'm a passionate environmental professional focused on climate change solutions, effective environmental communication, and responsible data analysis and visualization. I am a detail-oriented team player with managerial experience and a commitment to learning and growing. 

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Master of Environmental Science and Management", "2019-2021", "Bren School of Environmental Science & Management, University of California, Santa Barbara", "Santa Barbara, CA",
  "Bachelor of Arts", "2010-2014", "University of California, Santa Cruz", "Santa Cruz, CA"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Highlighted Coursework 

 * **Data:** Statistics & Data Analysis for Environmental Science & Management, Advanced Data Analysis, Geographic Information Systems (GIS)


 * **Economics, Law, & Policy:** Economics and Policy of Climate Change, Economics of Environmental Management, Environmental Law and Policy, Environmental Politics and Policy, Cost-Benefit Analysis and Non-market Valuation     



 * **Communication:** Writing Skills for Environmental Professionals, Advanced Environmental Communication, Survey Design and Environmental Public Opinion, Equity and the Environment     



 * **Energy & Climate:** Energy, Technology and the Environment, Climate Change Impacts and Adaptation, Earth System Science, Life Cycle Assessment (LCA)

# Master's Group Project
```{r}

tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Evaluating the climate mitigation potential of natural and working lands in Santa Barbara County", "2020-2021", "Client: County of Santa Barbara, Sustainability Division. Roles: Co-data manager, co-outreach manager", "Our team estimated county-wide carbon stocks and nitrous oxide emissions, projected land use change in working lands to create a baseline scenario, modeled forecasted changes to carbon stocks and emissions through land management scenarios, engaged with local experts, and recommended realistic greenhouse gas reduction strategies to the County",
) %>%
  detailed_entries(Degree, Year, Institution, Where)
```

# Professional Experience 

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Research & Engagement Intern", "2020", "Santa Barbara County Food Action Network", "Santa Barbara, CA",
  "Teaching Assistant (Sociology & Biology)", "2019-2020", "University of California, Santa Barbara", "Santa Barbara, CA",
  "Environmental Educator/Naturalist", "2015-2019", "Exploring New Horizons Outdoor School", "Loma Mar, CA",
  "Director", "2018", "Life Lab Summer Camp", "Santa Cruz, CA",
  "Ecuador Trip Co-Leader", "2017", "The Road Less Traveled", "Ecuador",
  "Assistant Director", "2015-2016", "Life Lab Summer Camp", "Santa Cruz, CA",
  "Naturalist Intern", "2014-2015", "Sierra Outdoor School", "Sonora, CA"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Additional Experience 

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Community Volunteer", "2017-2019", "Puente de la Costa Sur", "Pescadero, CA",
  "Conference Organizer", "2017-2019", "Pescadero Valley Conference", "Loma Mar, CA",
  "Ropes Course Facilitator", "2015-2019", "YMCA Camp Jones Gulch", "La Honda, CA"
  
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Skills and Certifications 

 * **Computer & Software:** Microsoft Office Suite (Excel, PowerPoint, Word), Google Workspace, R and RStudio, ArcGIS, Slack, Zoom, Trello
 
 * **Language:** Spanish (verbal and written proficiency), English fluency
 
 * **Certifications:** Wilderness First Responder, California Naturalist Program (2014)


```{r}
# tribble(
#   ~ Degree, ~ Year, ~ Institution, ~ Where,
#   "Computer & Software:", "", "Microsoft Office Suite (Excel, PowerPoint, Word), R and RStudio, ArcGIS, Slack, Zoom, Trello", "",
#   "Language:", "", "Spanish (verbal and written proficiency)", "",
#   "Certifications:", "", "Wilderness First Responder, California Naturalist Program (2014)", ""
# 
# ) %>% 
#   detailed_entries(Degree, Year, Institution, Where)
```
